Decade of Lost Precision: A General Framework For Image Feature Matching Without Geometric Constraints

### 2014-11-27 paper.tex
Fixed tau and added images

The empirical results of \emph{Self-Match} in Figure~\ref{fig:all_objects} and Figure~\ref{fig:patches} support the assumption. \emph{Self-Match} discards any match where a feature in the query image is more similar to the query feature, yet the algorithm consistently performs equally well or better than \emph{Ratio-Match} supporting the notion that for almost all true correspondences the best match is found in the \emph{target image}. As we would expect this assumption breaks down as we increase \tau to accept matches with higher uniqueness ratios, illustrated by the higher recall rates of \emph{Ratio-Match} compared to \emph{Self-Match} in most plots. Once we accept almost all proposed nearest neighbors as matches we are bound to encounter more non-distinct feature points for which even true correspondences might have better matches amongst the \emph{query features}.

>>>>

The empirical results of \emph{Self-Match} in Figure~\ref{fig:all_objects} and Figure~\ref{fig:patches} support the assumption. \emph{Self-Match} discards any match where a feature in the query image is more similar to the query feature, yet the algorithm consistently performs equally well or better than \emph{Ratio-Match} supporting the notion that for almost all true correspondences the best match is found in the \emph{target image}. As we would expect this assumption breaks down as we increase $\tau$ to accept matches with higher uniqueness ratios, illustrated by the higher recall rates of \emph{Ratio-Match} compared to \emph{Self-Match} in most plots. Once we accept almost all proposed nearest neighbors as matches we are bound to encounter more non-distinct feature points for which even true correspondences might have better matches amongst the \emph{query features}.
